---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

# coolors

Need a quick color palette for a plot or map in R? 

I use [coolors.co](https://coolors.co) multiple times a day to find color palettes. With how often I was visiting the site and exporting hex codes, I finally got around to writing this package containing a handful (currently ~2,000) of the site's five-color palettes.

## Installation

``` r
# install.packages("devtools")
devtools::install_github("simmwill/coolors")
```
## Basic usage

This simple package has two functions: generate a **coolors** color palette (randomly by default), and recall the current session's history of generated palettes. 

```{r, include = FALSE}
set.seed(12)
```


```{r example, fig.height=1}
library(coolors)

# generate a few random coolors palettes
palette_coolors()
palette_coolors()
palette_coolors()
# see history, with most recent at top of list
coolors_history()
```

## Other features

We can also use `palette_coolors(n = #)` to generate a palette shorter or longer than the default five. If shorter than five, the palette will simply be truncated; if longer, colors will be interpolated. 

Let's use one of the palettes we generated above and confirmed using `coolors_history()`: palette `336`. We can specify this identifier in the `palette_num` argument.

```{r example2, fig.height=1}
# 100-color palette (nearly a gradient)
palette_coolors(palette_num = 336, n = 100)
# 2-color palette (chooses the first two colors)
palette_coolors(palette_num = 336, n = 2)
```

Finally, if we just want the hex codes for a palette, we can use `hex = TRUE`.

```{r}
# generate hex codes for palette 336
palette_coolors(palette_num = 336, hex = TRUE)

```

## A fun plot

```{r, warning=FALSE, message=FALSE}
library(ggplot2)
library(palmerpenguins)

pal <- palette_coolors(palette_num = 123, hex = TRUE)

ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + 
  geom_point() + 
  scale_color_manual(values = pal) +
  theme_bw()
  
```


## Notes

All color palettes courtesy of [coolors.co](https://coolors.co) and its creator, [Fabrizio Bianchi](http://fabrizio.io/). This package also draws inspiration from several wonderful color palette packages, including `wesanderson`. 
